%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Stackoverflow CV
% LaTeX Template
% Version 1.0 (6/6/22)
%
% This class has been modified from a version originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
% Modified for Stackoverflow CV by Alessandra Bilardi (alessandra.bilardi@gmail.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{stackoverflow} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.7\textwidth} % 70% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	{\HUGE\textcolor{stackoverflow-name}{\textbf{Graziano Statello}}} % First name
	{\HUGE\textcolor{stackoverflow-name}{\textbf{}}} % Last name

\end{minipage}
\begin{minipage}[t]{0.3\textwidth} % 30% of the page width for the details
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{flushright}
		{\small
			{London, United Kingdom}\\
			{\href{mailto:grazianos86@gmail.com}{grazianos86@gmail.com}}\\
			{\href{https://github.com/Akallabet}{github.com/Akallabet}}\\
		}
	\end{flushright}
\end{minipage}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.1\textwidth}\vspace{\baselineskip}\hfill\end{minipage}
\begin{minipage}[t]{0.8\textwidth} % 40% of the page width for the introduction text
	\vspace{\baselineskip} % Required for vertically aligning minipages
	\vspace{\baselineskip} % Required for vertically aligning minipages
\end{minipage}
\begin{minipage}[t]{0.1\textwidth}\vspace{\baselineskip}\end{minipage}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\textcolor{stackoverflow}{\hrule}
\begin{minipage}[t]{0.25\textwidth}
	\vspace{\baselineskip} % Required for vertically aligning minipages
	\cvsect{Technical Skills}
\end{minipage}
\begin{minipage}[t]{0.75\textwidth}
	\vspace{\baselineskip} % Required for vertically aligning minipages
	{\normalsize\emph{I'm an experienced software engineer with a particular interest in web technologies.
	I have built and delivered performant and robust applications, using a variety of Agile methodologies.
	My main programming language is Javascript for both Front End and Back End, but I'm also interested in functional programming and started to use Clojure in the past year.
	}}\\\\
	{\small
		\miniblock{0.1}{0.9}{Likes:}
			{Javascript Nodejs Reactjs GraphQL Clojure AWS continuous-delivery Functional Programming\\}
	}
\end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\textcolor{stackoverflow}{\hrule}
\vspace{4pt} % Whitespace before the section title
\begin{tcolorbox}[blanker,width=0.75\textwidth,enlarge left by=0.25\textwidth,before skip=6pt,breakable,
	overlay unbroken and first={%
	  \node[inner sep=0pt,outer sep=0pt,text width=0.35\textwidth,
		align=none,
		below right]
		at ([xshift=-0.25\textwidth]frame.north west)
{
	\cvsect{Experience}
};}]
{\vspace{-16.3pt} % Whitespace before the section title
	\small\begin{entrylist}
	\entry
		{Mar 2023 → Now}
		{Senior Software Developer}
		{Nearform - Project: Mckinsey/Wave}
		{{Nodejs,  Reactjs, Playwright, AWS, Docker, Jenkins, elastic-search}\\\\
		Maintaining and improving a complex and multifaceted web based Saas platform }
	\entry
		{Aug 2021 → Mar 2023}
		{Senior Web Developer}
		{Signal AI}
		{{Nodejs, Graphql, Reactjs, Clojure, micro-frontends, Terraform, aws, docker, continuous-deployment, elastic-search}\\\\
		Developing pipelines across the full stack (FrontEnd, BackEnd, Database and Infrastructure) to optimise the delivery of advanced insights created from the consumption of millions of documents a day using Machine Learning and NLP.
		}
	\entry
		{Jan 2020 → Aug 2021}
		{Front End Technology Principal}
		{AND Digital}
		{{reactjs, gatsby, react-testing-library, cypress, amazon-web-services, github-actions, azure-devops, contentful, material-ui}\\\\
		Driving AND Digital technology offer by influencing the early adoption of key technologies such as headless CMS, GatsbyJs, NextJs and Graphql, which have been proven key in attracting and retaining customers. Successfully delivered key applications, resulting in newly developed business relationships. Training and mentoring junior and mid level developers.}
	\entry
		{Oct 2018 → Jan 2020}
		{Lead Front End Developer}
		{AND Digital}
		{{reactjs, react-testing-library, gatsby, node.js, github-actions}\\\\
		Leading multiple teams of developers for different web focussed projects, training and mentoring junior and mid level developers.}
	\entry
		{Oct 2017 → Oct 2018}
		{Product Developer}
		{AND Digital}
		{{frontend, ecmascript-6, javascript, reactjs}\\\\
		Tech Lead strongly Front End focussed, being responsible for the delivery of end to end projects}
	\entry
		{Mar 2016 → Aug 2017}
		{Senior Front End Developer}
		{ICAP}
		{{d3.js, reactjs, ecmascript-6, webpack, karma-runner, chai}\\\\
		I was part of multiple teams that built a real time trading platform used by brokers to arbitrate buying and selling of various financial products.
My team was responsible for the web platform which we built using microFrontends in React and Redux, we used D3 to create custom charts. We used CI/CD with multiple daily releases and whilst monitoring performance, quality and security.}
	\entry
		{Mar 2014 → Mar 2016}
		{Javascript Developer}
		{VML London}
		{{angularjs, css, javascript, git, gruntjs, gulp, protractor, karma-runner, jasmine}\\\\
		I was involved in the modernisation and revamping of http://www.premierinn.com using Adobe Experience Manager and AngularJs, improving SEO visibility, first time loading speed and allowing multi language customisation for german market.
		We ran Continuous Integration with multiple daily releases, canary releases and traffic monitoring.}
	\entry
		{Feb 2012 → Apr 2014}
		{Front end Engineer}
		{Offerte Tour Operator}
		{{javascript, php, slim, angularjs, css}\\\\
		Worked as a web developer for a small and dynamic startup that has distrupted the travel \& tourism industry in Italy. I've been responsible for the creation and maintenance of a highly flexible whitelable used in a variety of travel agencies websites.}
	\end{entrylist}}
\end{tcolorbox}

%----------------------------------------------------------------------------------------
%	APPS & Software
%----------------------------------------------------------------------------------------

\textcolor{stackoverflow}{\hrule}
\vspace{4pt} % Whitespace before the section title
\begin{tcolorbox}[blanker,width=0.75\textwidth,enlarge left by=0.25\textwidth,before skip=6pt,breakable,
	overlay unbroken and first={%
	  \node[inner sep=0pt,outer sep=0pt,text width=0.35\textwidth,
		align=none,
		below right]
		at ([xshift=-0.25\textwidth]frame.north west)
{
	\vspace{\baselineskip} % Whitespace before the section title
	\cvsect{Apps \& Software}
};}]
{\vspace{-16.3pt} % Whitespace before the section title
	\small\begin{entrylist}
	\entry
		{Mar 2021}
		{Order and Pay at Table app - Zizzi and ASK Italian}
		{\href{https://pronto.askitalian.co.uk}{https://pronto.askitalian.co.uk}}
		{{node.js, gatsby, material-ui, websocket, cypress, react-testing-library, koa, microservices}\\\\
		Lead a fully remote team in building an ambitious mobile-first website for ordering and paying at table for Zizzi and Ask Italian. The result was a sound success and we had the highest adoption rate of any other similar product in the UK. We used GatsbyJs on a bespoke microservices AWS architecture and real time communication with the use of web-sockets.}
	\entry
		{Jul 2020}
		{Premier Inn Business}
		{\href{https://www.premierinn.com}{https://www.premierinn.com}}
		{{reactjs, cypress, aem}\\\\
		Lead multiple teams to deliver the business facing website of Premierinn. This was a complex project where we had to migrate existing functionalities from AEM to a modern REST/React stack, we achieved that to use cypress and cucumber to provide a solid layer of E2E tests on the existing website, while extending it with the business side.}
	\entry
		{May 2020}
		{Restoration \& Renewal Programme}
		{\href{https://restorationandrenewal.uk}{https://restorationandrenewal.uk}}
		{{reactjs, cypress, aem}\\\\
		I lead a team on a fast paced 3 months project for the Westminster Restoration \& Renewal programme. We've built a website with Gatsbyjs, based on a bespoke Azure architecture, using Contentful as headless CMS. The result was a high performance, fully accessible and SEO optimised website. The project was considered a success and allowed AND to be considered a major technology partner for the public sector.}
	\entry
		{Sep 2019}
		{AVON Recruitment Platform}
		{}
		{{reactjs, material-ui, jest, azure-devops, react-testing-library}\\\\
		Lead team that built a market agnostic AVON Sales Leaders recruitment websites (and App) with admin, in collaboration 3rd parties from different parts of the world}
	\entry
		{Oct 2018}
		{Lloyds}
		{}
		{{reactjs, react-native}\\\\
		Add new features for the Lloyds App (IOs and Android)}
	\end{entrylist}}
\end{tcolorbox}
\end{document}
